Community-Conditioned Language Models

### 2020-10-29 paper/paper.tex
training scheme

>>>>

We combined the 46 community corproa and split the combined corpus,
reserving 10\% for testing, 10\% for validation and the rest for training.
Splits were stratified by community so that the same number of training examples
were available for each community.

We used a vocabulary size of \num{40000} tokens, with a special out-of-vocabulary token.
The vocabulary consisted of the most frequent tokens at the comment level,
meaning that we only counted each token once per comment.
The main reason for this was to avoid over-counting otherwise rare tokens that were spammed
many times in a single comment.

We trained the models on a simple left-to-right language modeling task 
with cross entropy loss over the vocabulary 
and AdamW \citep{Loshchilov2019} optimization, with an inital learning rate of \num{0.001}.
We used a batch size of \num{256} and a maximum sequence length of \num{64} tokens.
During training, a dropout rate of $0.1$ was applied between encoder layers 
and after each linear layer.

All experiments used models with \num{3} sequence encoder layers, 
each with hidden (and token embedding) size of \num{256}. 
The transformer models had \num{8} attention heads per layer.\footnote{
  This number of attention heads was chosen to give the LSTM and transformer
  models a comparable number of paramters 
  (\num{22171203} and \num{21779523}, respectively).}
The conditional models were given a community embedding with \num{16} dimensions.

We trained the models until the validation loss was smaller than the smallest
validation loss for two epochs in a row. 
The weights from the epoch with the smallest validation loss were used for testing.
